---
title: "R Notebook"
output: html_notebook
---


Task 1.
Load the data again, clean_names(), and re-familiarise yourself with it

```{r}
library(tidyverse)
library(janitor)
ames <- read_csv("data/ames.csv") %>% clean_names()

ames
```


Task 2.
Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?

```{r}
ames %>% 
  ggplot(aes(lot_area)) +
  geom_histogram()
```

The distribution is not normal, there are many small outliers that skew to the
right. We can say that it is unimodal distribution. 

Task 3.
Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.


```{r}
library(infer)


bootstrap_mean_lot_area <- ames %>% 
  specify(response = lot_area) %>% 
  generate(reps = 4000, type = "bootstrap") %>% 
  calculate(stat = "mean")

bootstrap_mean_lot_area %>% 
  visualise(bins = 30)
  
```



Task 4.
Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution

```{r}
bootstrap_ci95 <- bootstrap_mean_lot_area %>% 
  get_ci(level = 0.95, type = "percentile")

bootstrap_mean_lot_area %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = bootstrap_ci95)
```


Task 5.
You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95% CI? Does that make sense?

```{r}

bootstrap_ci99 <- bootstrap_mean_lot_area %>% 
  get_ci(level = 0.99, type = "percentile")

bootstrap_mean_lot_area %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = bootstrap_ci99)
```

this confidence interval is broader. This makes sense because we are looking at all
the data within the 99% confidence interval. So we can say with confidence that
most of the data falls within this range. 


Task 6.
Calculate the point estimate of the mean(lot_area)

```{r}
bootstrap_mean_lot_area %>% 
  summarise(
    mean = mean(stat)
  )
```

