---
title: "R Notebook"
output: html_notebook
---

Question 1.
Load the code_clan_tweets.csv data. Find the number of rows, columns, and list all the variable names.

```{r}
library(tidyverse)

clan_tweets <- read.csv("data/code_clan_tweets.csv")

clan_tweets

dim(clan_tweets)
names(clan_tweets)
view(clan_tweets)
```



Question 2.
Find the total number of favourites (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).


```{r}
clan_tweets %>% 
  select(favorite_count, is_quote) %>% 
  filter(is_quote == FALSE) %>% 
  summarise(total = sum(favorite_count))
```



Question 3.
Summarise the mean number of retweets (retweet_count), split by the type of platform that was used to tweet (source). Again, omit quoted tweets from the mean.

```{r}
clan_tweets %>% 
  select(retweet_count, source, is_quote) %>% 
  filter(is_quote == FALSE) %>% 
  group_by(source) %>% 
  summarise(mean(retweet_count)) %>% 
  ungroup()
```

Question 4.
Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.

```{r}
clan_tweets %>% 
  select(favorite_count, media_type) %>% 
  mutate(media_type = coalesce(media_type, "text")) %>% 
  group_by(media_type) %>% 
  summarise(total_count = sum(favorite_count))
  
```


Question 5.
Find the mean number of characters that a CodeClan tweet contains. You can either find a way to count the text in the text variable, or use the variable display_text_width which contains a count. Checking both would be a good idea if possible to see if they match (but it’s not essential).

```{r}
clan_tweets %>% 
  mutate(character_n = str_length(text)) %>% 
  summarise(mean(character_n)) %>% 
  pull()
```



Question 6.
The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}

code_info <- read_csv("data/code_clan_info.csv")

code_info
clan_tweets

code_info <- inner_join(clan_tweets, code_info, c("tweet_id" = "tweet_id"))
```




Question 7.
From your new joined data, create a new tibble codeclan_hashtags containing only tweet_id and hashtags, then convert hashtags into lowercase for analysis. Keep only those tweets with hashtags.

```{r}
codeclan_hashtags <- code_info %>% 
  select(tweet_id, hashtags) %>% 
  mutate(hashtags = str_to_lower(hashtags)) %>% 
  filter(!is.na(hashtags))

codeclan_hashtags
```

Question 8.
Some tweets have more than one hashtag, denoted by the c( symbols at the start of the string. Use the str_sub() and str_detect() functions and your codeclan_hashtags tibble from above to find all the cases in which the hashtag string begins with charactersc(.

```{r}

## Corrected using answers: originally didn't get an answer as was not sure how to
## combine the str_sub and str_detect functions

hashtags_multiple <- codeclan_hashtags %>% 
  mutate(first_letters = str_sub(hashtags, 1, 2)) %>%
  filter(str_detect(first_letters, "c\\("))


## OR


codeclan_hashtags %>% 
  filter(str_detect(hashtags, "c\\("))

```

Question 9.
Use the str_detect() function to find all tweets with text that mentions “Edinburgh”, and count how many such tweets there are.


```{r}

## Originally got 8 but that was because I was using the wrong data, was using
## the hashtag data and not tweet data. 

codeclan_hashtags

clan_tweets %>% 
  mutate(lower_case_edi = str_to_lower(text)) %>% 
  filter(str_detect(lower_case_edi, "edinburgh")) %>% 
  summarise(count = n())
  
 

```



Question 10.
Use str_extract_all() with a regular expression to find out which Twitter users CodeClan have been tweeting.

```{r}

## Didn't get an answer for this as wasn't too sure how to use the pattern object

# twitter handle is an @ followed by a bunch of letters numbers and other symbols

user_pattern <- "@[a-zA-Z0-9_]+"
tweets <- clan_tweets %>% 
  select(text)
head(str_extract_all(clan_tweets$text, user_pattern))
```

