---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

##########
load in libraries
##########

```{r}
library(tidyverse)
library(janitor)
library(lubridate)
```

#########
load in data
#########

```{r}
transaction <- read_csv("raw_data/toy_transactions.csv") 
```

############
question 1
############

```{r}
transaction <- transaction %>% 
  unite("date", day:year, remove = TRUE) %>% 
  mutate(date = dmy(date))
```

###########
question 2
###########

```{r}
toys <- read_csv("raw_data/toys.csv")
```

```{r}
toys <- toys %>% 
  mutate(weight = str_replace_all(weight, "g", ""),
         weight = as.numeric(weight)) %>% 
  separate(product, into = c("product_name", "product_title"), sep = "-")
```

```{r}
quality <- read_csv("raw_data/quality.csv")
```

```{r}
quality <- quality %>% 
  mutate(description = str_replace_all(description, "Quality: ", ""),
         description = case_when(
           description == "Very Awesome" ~ "Very Good",
           description == "Awesome" ~ "Good",
           description == "Awful" ~ "Bad",
           description == "Very Awful" ~ "Very Bad",
           TRUE ~ description
         ))
```


##########
question 4
##########

```{r}
customer_data <- "../Day 5/raw_data"

fs::dir_ls(customer_data)

csv_files <- fs::dir_ls(customer_data, regexp = "\\mers.csv$")

```

```{r}
customers <- csv_files %>% 
  map_dfr(read_csv)
```

##########
question 5
##########

Impute missing values in numeric columns with the median value of customers with 
the same gender and country. For example, a customer whose gender is female and 
whose country is Australia with a missing age should get the median age of all 
Australian females in the dataset.

Hint: You can combine a group by() with mutate(across()) to apply coalesce across 
columns which meet a logical criteria specified with where(). Also remember, in 
across() we can define our own anonymous function like so ~ mean(.x, na.rm = TRUE) 
where the .x represents what is being iterated on (when using across, this is the columns).

```{r}
customers <- customers %>% 
  group_by(customer_country, customer_gender) %>% 
  mutate(
    across(where(is.numeric) & !id,
           ~coalesce(.x, mean(.x, na.rm = TRUE)))) %>% 
  ungroup()

```


```{r}
transaction
toys 
quality
customers
```

############
question 7
############

# join all the datasets

```{r}
join_1 <- full_join(customers, transaction, by = c("id" = "customer_id")) 

join_2 <- full_join(toys, quality, by = c("quality" = "id"))

join_1
join_2
```

```{r}
toys_joined <- full_join(join_1, join_2, by = c("toy_id" = "id"))
```


##########
question 8
##########

Ethical considerations are that there is a security threat given all data is now
kept in the same place therefore if there was a security breach, all information
on a customer would be easily accessible. 

Customer names are available so can easily identify customers

##########
question 9
##########

```{r}
new_toys_joined <- toys_joined %>% 
  select(-first_name, -last_name)
```

############
question 10
############

```{r}
write_csv(new_toys_joined, "../Day 5/toys_joined.csv")

```



