---
title: "R Notebook"
output: html_notebook
---

#########
load libraries
#########

```{r}
library(tidyverse)
library(janitor)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(broom)
```

#########
load data
#########

```{r}
prog_man <- read_csv("data/project_management.csv")
prog_man
```
#########
task 1
#########

```{r}
prog_man %>% 
  ggplot(aes(estimated_length, actual_length)) +
  geom_point()
```

#########
task 2
#########

```{r}
prog_man %>% 
  summarise(cor(estimated_length, actual_length))
```
strong positive correlation between estimated length and actual length.


#########
Task 3
#########

```{r}
lm1 <- prog_man %>% 
  lm(formula = actual_length ~ estimated_length)

lm1
```

#########
Task 4
#########

```{r}
tab_model(lm1)
```

for every increase in estimated height by 1cm, corresponds with a 1.22cm increase
in actual length on average

R^2 - 0.647 

This suggests that the model is a good fit


##########
Task 5
##########

```{r}
tidy_output <- tidy(lm1)
glance_output <- glance(lm1)

tidy_output
glance_output
```

p-value = <0.001

there is a statistically significant relationship between the two and thus we 
cannot reject the null hypothesis 