---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(ggplot2)

```

```{r}
back_pack <- CodeClanData::backpack

back_pack
```

Question 1.

Load in the libraries you need, and look at the backpack data. Take note of variable names and dimensions.


```{r}
back_pack

names(back_pack)
dim(back_pack)
```


Question 2.

What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}
back_pack %>% 
  ggplot() +
  aes(x = backpack_weight) +
  geom_histogram(binwidth = 5, col = "white") 
```
There is a normal distribution of backpack weight among students with the most
occuring at a weight of 10 and 0 occuring at 30. 

Question 3.

Are there differences in backpack weight between sex?


```{r}
back_pack %>% 
  ggplot() +
  aes(x = backpack_weight) +
  geom_histogram(binwidth = 5, col = "white") +
  facet_wrap(~sex)
```

Females account for most weight categories less than 20. Where as Males make up
most of the heavier weight values.

Question 4.

What is the relationship between body weight and backpack weight?


```{r}
back_pack %>% 
  ggplot() +
  aes(x = body_weight, y = backpack_weight) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE)
```

There is a small positive correlation between body weight and backpack weight.
However, there are numerous outliers in the scatterplot indicating that someone
who has a heavier body weight does not mean they will carry a larger backpack
weight. 

Question 5.

Is this relationship different between men and women? Choose an appropriate plot and interpret your findings.

```{r}
back_pack %>% 
  ggplot() +
  aes(x = body_weight, y = backpack_weight, colour = sex) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE)
```


Females demostrate a more correlated relationship between body weight and 
backpack weight when compared with Males. Therefore, a Male's use of heavier
weight is less explained by this graph than Females. 


Question 6.

What proportion of students report back pain?


```{r}
back_pack %>% 
  ggplot( aes(x = back_problems)) +
  geom_bar() +
  scale_x_continuous(breaks = seq(0, 1))
```
From the graph, it shows that approximately a third of people reported back pain

Question 7.

Is this proportion different between men and women?


```{r}
back_pack %>% 
  ggplot( aes(x = back_problems, fill = sex)) +
  geom_bar(position = "dodge") +
  scale_x_continuous(breaks = seq(0, 1))
```

When gender is factored in, we can see the majority of people reporting back
problems were females whereas most people reporting no problems were male 
although the numbers are similar. 

Question 8.

Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.


```{r}
back_pack %>% 
  filter(back_problems == 1) %>% 
  ggplot() +
  aes(x = body_weight, y = backpack_weight) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  facet_wrap(~sex)
```

Females with reported back problems display a positive relationship with lots of 
outliers indicating there is a poor correlation between the two variables. 

Males have a negative relationship, displaying that as body weight increases
backpack weight decreases. 