---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(infer)
```

# question 1 and 2

H0: they do not differ
H1: they differ

H0: mean_sleep_total - mean_jabber_sleep == 0
H1: mean_sleep_total - mean_jabber_sleep != 0 

```{r}
data(msleep)

avg_sleep <- msleep %>% 
  # find the mean of sleep_total for the sample population
  summarise(mean_sleep_total = mean(sleep_total))

avg_sleep

# mean_sleep_total == 10.4
# differs by 3.4 on average

q1_null_distribution <- msleep %>% 
  specify(response = sleep_total) %>% 
  hypothesise(null = "point", mu = 7) %>% 
  generate(type = "bootstrap", reps = 2000) %>% 
  calculate(stat = "mean")

q1_null_distribution %>% 
  visualise(bins = 30)

q1_null_distribution %>% 
  visualise(bins = 30) +
  shade_p_value(obs_stat = avg_sleep$mean_sleep_total,
                direction = "both")

q1_null_distribution %>% 
  get_p_value(obs_stat = avg_sleep$mean_sleep_total,
                direction = "both")

```

p-value is close to 0 which means we can reject the null hypothesis at the
0.01 level of significance. 

# question 3

H0: Omnivores DO NOT sleep significantly longer than herbivores
H1: Omnivores DO sleep significantly longer than herbivores

HO: mean_omni_sleep - mean_herb_sleep == 0
H1: mean_omni_sleep - mean_herb_sleep > 0

```{r}

observed_stat <- msleep %>% 
  filter(vore %in% c("omni", "herbi")) %>%
  specify(sleep_total ~ vore) %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))

# 10.93 - 9.51 = 1.42
# there is a statistically significant difference 

# need to add in level of significance and model the null hypothesis
# question only says statistical test though

observed_stat %>% 
  ggplot() +
  aes(x = vore, y = mean_sleep_vore) + 
  geom_col()

q3_null_distribution <- msleep %>% 
  filter(vore %in% c("omni", "herbi")) %>% 
  specify(sleep_total ~ vore) %>% 
  hypothesise(null = "independence") %>% 
  # permute shuffles the location variable because price should be`unaffected by location
  generate(reps = 10000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi")) 
  


q3_null_distribution %>% 
  visualise() + 
  shade_p_value(obs_stat = observed_stat$stat, 
                direction = "right")

q3_null_distribution %>% 
  get_p_value(obs_stat = observed_stat$stat,
              direction = "right")

```

# question 4

H0: prop_domesticated - 0.05 <= 0
H1: prop_domesticated - 0.05 > 0 


```{r}
sleep_domesticated <- msleep %>% 
  mutate(is_domesticated = if_else(conservation == "domesticated", 
                                   "domesticated",
                                   "not domesticated")) %>% 
  filter(!is.na(is_domesticated))

q4_stat <- sleep_domesticated %>% 
  summarise(prop_domesticated = sum(is_domesticated == "domesticated") / n())

q_4_null_distribution <- sleep_domesticated %>% 
  specify(response = is_domesticated,
          success = "domesticated") %>% 
  hypothesise(null = "point", p = 0.05) %>% 
  generate(reps = 10000, type = "draw") %>% 
  calculate(stat = "prop")

q_4_null_distribution %>% 
  visualise() + 
  shade_p_value(obs_stat = q4_stat$prop_domesticated,
                direction = "right")

q_4_null_distribution %>% 
  get_p_value(obs_stat = q4_stat$prop_domesticated,
                direction = "right")


```

## 1.2 Defining the hypothesis

For the next few questions, write out: 

- what kind of test would I use
- H0 and H1 in both mathematical notation and in words
- state the method to generate the null distribution

defintions for generate function: 

__bootstrap__ - sample is drawn from each replicate (can have thousands of different 
samples from the same dataset - creates a more normal distriution)

__permutation__ - each input (e.g. location == c(nice, corfu)) will be reassigned 
randomly to unchanged price data because the our hypothesis dictates price should
not depend on the location input. 

__draw__ - value is sampled from theoretical distribution with a parameter p 
specified in the hypothesise() function - only for testing on one proportion
statistic. 


# question 1. 


test: proportion test

H0: prop_survey - 0.4 = 0
H1: prop_survey - 0.4 > 0 

H0: The proportion of people who know about the shop in the town is LESS THAN 40
percent

H1: The proportion of people who know about the shop in the town is GREATER THAN
OR EQUAL to 40 percent 

generate(type = "draw") 


# question 2: 

test: proportion test


H0: website users are LESS likely to click on the banner if positioned at the 
top of the page

H1: website users are MORE likely to click on the banner if positioned at the 
top of the page

H0: prop_top - prop_side = 0 
H1: prop_top - prop_side > 0 

generate(type = "permute") 

- website should be unaffected by position of the banner



# question 3: 

test: mean

H0: The width of the sample data on parts DOES NOT differ significantly from 145mm
H1: The width of the sample data on parts DOES differs significantly from 145mm


H0: mean_diff_width == 145 
H1: mean_diff_width != 145 


generate(type = "bootstrap")


## 1.3 - Interpreting results

p-value > level of significance -> DO NOT reject H0 

p-value <= level of significance -> DO reject H0 

# question 1

0.07 > 0.05 

cannot reject the null hypothesis at the 0.05 level of significance


# question 2

0.006 < 0.01 

reject the null hypothesis at the 0.01 level of significance

# question 3

0.55 > 0.05

cannot reject the null hypothesis at the 0.05 level of significance


## Extension

question 1

```{r}
transactions <- read_csv("data/online_retail_subset.csv")

transactions
```


```{r}
transactions <- transactions %>% clean_names()

num_transactions <- transactions %>% 
  summarise(n = n_distinct(invoice_no))
  
```

```{r}
support_a <- transactions %>% 
  filter(stock_code == 22469) %>% 
  summarise(support_a = n_distinct(invoice_no) / num_transactions) %>% 
  pull()

support_a
```

question 2

```{r}
support_a_b <- transactions %>% 
  summarise(support_a_b = (sum(stock_code == 22469) + sum(stock_code == 21110)) / n())
```

```{r}
confidence_a_b <- support_a_b / support_a

confidence_a_b
```

support_a_b == 1.13


question 3

```{r}
support_b <- transactions %>% 
  summarise(support_b = sum(stock_code == 21110) / n())

```

```{r}
lift_a_b <- support_a_b / support_a * support_b

lift_a_b
```

