---
title: "R Notebook"
output: html_notebook
---

```{r}
library(ggplot2)
library(tidyverse)
library(janitor)
```

```{r}
revenue <- CodeClanData::qb_revenue_breakdown %>% clean_names()

revenue
```

Question 1.
Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset.


```{r}
revenue %>% 
  ggplot() +
  geom_bar(aes(x = year, y = revenue, fill = product), stat = "identity") +
  labs(x = "Year", y = "Revenue")
```


Question 2.
Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year. This data is inside qb_monthly_sales, but you will need to use filter() or subset() (base R).

```{r}

sales <- CodeClanData::qb_monthly_sales %>% clean_names()

sales

kwikbit <- sales %>% 
  filter(cashflow == "Kwikbit Unit 1 Sales") 

kwikbit %>% 
  ggplot(aes(x = date, y = amount)) +
  geom_line() + 
  geom_point()

sales
```



Question 3.
Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.


```{r}
sales %>% 
  filter(!cashflow == "Kwikbit Unit 1 Sales") %>% 
  ggplot(aes(x = date, y = amount, group = cashflow, colour = cashflow)) +
  geom_line() + 
  geom_point()
  
```



Question 4.
Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors.


```{r}
competitors <- CodeClanData::qb_competitors %>% clean_names()

competitors

competitors %>% 
  ggplot(aes(x = year, y = revenue, fill = company, colour = company)) +
  geom_area() +
  scale_y_continuous(labels = scales::comma) 
```


Question 5.
Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines.


```{r}


competitors %>% 
  ggplot(aes(x = year, y = revenue, group = company, colour = company)) +
  geom_line() + 
  geom_point()
```


Question 6.
Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. The data for this is in qb_device_data.


```{r}
device <- CodeClanData::qb_device_data

device

## didn't read the question at all 

device %>% 
  rownames_to_column("time") %>% 
  ggplot(aes(x = time, y = counts)) +
  geom_line() +
  facet_wrap(~device)

## Answer

qb_device_data <- 
mutate(qb_device_data, decimal_hour = hours + (mins/60))

ggplot(qb_device_data) +
  aes(x = decimal_hour, y = counts) +
  geom_line() + 
  facet_grid(id ~ device)
```

