---
title: "R Notebook"
output: html_notebook
---

#######
load libraries
#######

```{r}
library(tidyverse)
library(janitor)
```

########
load in data
########

```{r}
customers <- read_csv("data/mall_customers.csv") %>% clean_names()
```


You have been provided some customer data from a shopping centre. 
Do some exploratory analysis on the data. Comment on findings.

```{r}
# avg income per gender
customers %>% 
  group_by(gender) %>% 
  summarise(avg_income = mean(annual_income_k))
```

```{r}
# avg income for each age
customers %>% 
  group_by(age) %>% 
  summarise(avg_income = mean(annual_income_k)) %>% 
  ggplot(aes(age, avg_income)) + 
  geom_col() +
  theme_classic()
```

```{r}
customers
```


We are interested in creating a marketing campaign to target customers based 
on their spending score and annual income. Perform a k-means clustering to find 
if there are meaningful clusters in the data to target the customers.

```{r}
# visualise two variables

customers %>% 
  ggplot(aes(annual_income_k, spending_score_1_100)) + 
  geom_point()
```
looks like some crazy data 

```{r}
customers_subset <- customers %>% 
  select(annual_income_k, spending_score_1_100) %>% 
  mutate(across(everything(), scale))
```

```{r}
cluster <- kmeans(customers_subset,
       centers = 4, # number of clusters
       nstart = 25) 
```


```{r}
library(factoextra)
```

first method: __Elbow Method__

```{r}
fviz_nbclust(customers_subset,
             kmeans,
             method = "wss",
             nstart = 25)
```

If the line is an arm, where is the elbow? Maybe at k = 2 or k = 3?


Method 2 - __Silhouette Coefficient__ 

```{r}
fviz_nbclust(customers_subset,
             kmeans,
             method = "silhouette",
             nstart = 25)
```

average distance between clusters. Higher means clusters are more distinct.

More evidence k = 2 is the optimal number of clusters 

method 3 - __Gap statistic__

```{r}
fviz_nbclust(customers_subset,
             kmeans,
             method = "gap",
             nstart = 25)
```


# create the cluster 

```{r}
library(broom)

# look at tidy output (centres)

tidy(cluster)

augment(cluster, customers_subset)

glance(cluster)


```



```{r}
# customers_subet is the scaled data set
# need to create a data set with the two variables I want 

customers_two_var <- customers %>% 
  select(annual_income_k, spending_score_1_100)

k_clusters <- tibble(k = 1:20) %>% 
  mutate(
    kclust = map(k, ~kmeans(x = customers_subset, centers = .x, nstart = 25)),
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, ~augment(.x, customers_two_var))
  )

k_clusters
```


```{r}
customers_subset

k_clusters %>% 
  unnest(augmented) %>% # explode column
  filter(k == 5) %>% # filter for optimal K 
  ggplot(aes(annual_income_k, spending_score_1_100, colour = .cluster, shape = .cluster)) +
  geom_point(size = 3) +
  theme_classic()
```
5 clusters seems like a good fit for the data, silhouette method recommended 5

data seems like a good fit for clustering, 5 distinct groups easily binned

labels: 

bottom left - low income / low spending score (fiscally responsible)
bottom right - high income / low spending score (savers)
centre - medium income / medium spending score
top left - low income / high spending score (irresponsible spenders)
top right - high income / high spenders 



Comment on the attributes on one or two of the clusters (maybe even give them a label if you like - like in section 4.1 of the ‘Segmentation & clustering intro’ lesson).


