---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(gtools)
source('../../../codeclan_work/Week 6/Day 1/prob.R')
```

```{r}
titanic <- read_csv("titanic.csv")

titanic
```

```{r}
titanic %>% 
  distinct(class)

# Feel like it needs to be divided by the total passengers survived, not total 
# number of passengers 

titanic %>% 
  count(class)

# this doesnt work 
titanic %>% 
  mutate(passenger_crew = if_else(class == c("deck crew", "engineering crew", "restaurant staff", "victualling crew"), "crew", "passenger")) %>% 
  count(passenger_crew)
  
  select(survived, passenger_crew) %>% 
  group_by(passenger_crew) %>% 
  summarise(sum(survived == "yes")/ n())


```

```{r}
titanic %>% 
  mutate(passenger_crew = if_else(class == c("3rd", "2nd", "1st"), "passenger", "crew")) %>% 
  select(survived, passenger_crew) %>% 
  filter(passenger_crew == "crew", survived == "yes") %>% 
  summarise(prob = n() / nrow(titanic))
```

Question 1.
If I roll a six-sided dice once, what is the probability of getting a number less than 5?


```{r}
4/6
2/3
```


Question 2.
How many outcomes are there in the sample space of an experiment in which we toss three dice?

```{r}
three_dice <- rolldie(3) %>% 
  summarise(outcomes = n())

three_dice
```

Question 3.
In an experiment where we roll four dice:

how many outcomes are in the event where the total of the four dice equals 5, 6 or 7)?
what is the probability of this event?
what assumptions do we apply in answering part ii?


```{r}
roll_four <- rolldie(4) %>% 
  mutate(total = rowSums(.))

roll_four %>% 
  filter(total == c(5, 6, 7)) %>% 
  nrow()
```

Question 4.
Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

```{r}



chair_1 <- c(1,2,3,4,5)
chair_2 <- c(2,3,4,5,1)
chair_3 <- c(3,4,5,1,2)
chair_4 <- c(4,5,1,2,3)
chair_5 <- c(5,1,2,3,4)

chairs <- data_frame(chair_1, chair_2, chair_3, chair_4, chair_5)

chairs



1/120

```

Question 5.
I roll six dice:

what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?
what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?

```{r}
six_dice <- rolldie(6)

six_dice %>% 
  isin(c(1,2,3,4,5,6), ordered = FALSE)

# wasnt too sure how to yse the isin() function 
```

If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades?

```{r}
library(janitor)

deck <- cards() %>% as.tibble()

deck

deck %>% 
  mutate(black_red = case_when(
    suit == "Club" ~ "black",
    suit == "Spade" ~ "black",
    TRUE ~ "red"
  )) %>% 
  filter(black_red == "black", suit == "Spade") %>% 
  summarise(prob = n() / nrow(deck))

# this equation explains if taken from entire deck 

50/50 #if specific to the question 
```

