---
title: "R Notebook"
output: html_notebook
---

```{r}
library(janitor)
library(tidyverse)
```



Question 1.
Load the data, clean_names() and explore it.

```{r}
phones <- read.csv("data/20190928-items.csv") %>% clean_names()
```


Question 2.
Find the brand with the highest numbers of phones in the dataset.


```{r}
phones %>% 
  group_by(brand) %>% 
  summarise(total_phones = n()) %>% 
  slice_max(total_phones)
```

Question 3.
For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. 

```{r}
samsung <- phones %>% 
  filter(brand == "Samsung") %>% 
  select(rating)
  #mutate(log_rating = log(rating)) %>% 
  #filter(!log_rating == 0.0000000)

samsung
```

```{r}
samsung_rating_stats <- samsung %>% 
  summarise(
    mean = mean(rating),
    sd = sd(rating)
  )

samsung_rating_stats
```

```{r}
samsung %>% 
  ggplot(aes(rating)) +
  geom_histogram(aes(y = ..density..), fill = "red", col = "red", bins = 30) +
  stat_function(
    fun = dnorm,
    args = list(
      mean = samsung_rating_stats$mean,
      sd = samsung_rating_stats$sd
    ),
    col = "steelblue",
    size = 1.2
    )
```

Do you think the normal distribution provides a good model of these ratings?

I think it does, it shows the spread of ratings with a nice 'bell-shaped' curve
which will aid in future analysis. Could transform ratings data to natural
logarithms to create a more normal distribution. 

Question 4.
We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the mean() and sd() of your distribution in an earlier question. Use these values to calculate the proportions of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution.


```{r}
samsung %>% 
  # within how many sd of mean is each value? 
  # mutate(log_rating = log(rating)) %>% 
  mutate(x_rating = scale(rating)) %>% 
  # return TRUE if it is within 1 else FALSE etc. 
  mutate(within_one_sigma = if_else(abs(x_rating) <= 1, TRUE, FALSE),
         within_two_sigma = if_else(abs(x_rating) <= 2, TRUE, FALSE),
          within_three_sigma = if_else(abs(x_rating) <= 3, TRUE, FALSE)) %>%
  # return sum of sd rating within 1/2/3 sd divided by the number of obs
  # basically looking for the percentage of ratings within 1/2/3 standard deviations 
  summarise(
    n_within_one = sum(within_one_sigma)/n(),
    n_within_two = sum(within_two_sigma)/n(),
    n_within_three = sum(within_three_sigma)/n()
    )
```

Compare these proportions with those you expect for a normal distribution.

The normal distribution expects 68.5% of data to be spread across 1 sd. In this
data, we see that 79% is within the first sd. 



