---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
```

```{r}
titanic_data <- read_csv("data/titanic_decision_tree_data.csv") %>% clean_names()
```

```{r}
library(rpart)
library(rpart.plot)

shuffle_index <- sample(1:nrow(titanic_data))

# shuffle the data so class order isn't in order - need this for training/testing split later on 
titanic_set <- titanic_data[shuffle_index, ]
```


Take only observations which have a survived flag (i.e. that aren’t missing)
Turn your important variables into factors (sex, survived, pclass, embarkation)
Create an age_status variable which groups individuals under (and including) 
16 years of age into a category called “child” category and those over 16 into 
a category called “adult”.
Drop the NA
Drop any variables you don’t need (X1, passenger_id, name, ticket, far, cabin)

```{r}
titanic_set

titanic_set <-  titanic_set %>%
  filter(!is.na(survived)) %>% 
  mutate(across(.cols = c(sex, survived, pclass, embarked), 
                .fns = as_factor)) %>% 
  mutate(age_status = as_factor(if_else(age > 16, "adult", "child"))) %>% 
  select(-c(x1, passenger_id, name, ticket, fare, cabin)) %>% 
  drop_na()

titanic_set <- titanic_set %>% 
  mutate(survived = if_else(survived == 0, "No", "Yes"),
         pclass = case_when(
           pclass == 1 ~ "Upper",
           pclass == 2 ~ "Middle",
           pclass == 3 ~ "Lower"
         ))

titanic_set <- titanic_set %>% 
  select(survived, everything())

titanic_set %>% 
  mutate(survived = as_factor(survived))
  
```

```{r}
glimpse(titanic_set)
```

```{r}
library(GGally)

titanic_set %>% 
  ggpairs()
```

class, age , age status?


```{r}
# get how many rows we have in total to work out the percentage
n_data <- nrow(titanic_set)

# create a test sample index
test_index <- sample(1:n_data, size = n_data*0.2)

# create test set
titanic_test  <- slice(titanic_set, test_index)

# create training set
titanic_train <- slice(titanic_set, -test_index)
```


# check the amount of people that survived and who didnt survive for train/test

```{r}
titanic_test %>%
 janitor::tabyl(survived)

titanic_train %>% 
  janitor::tabyl(survived)
```

```{r}
titanic_fit <- rpart(
  formula = survived ~ ., 
  data = titanic_train, 
  method = 'class'
)

rpart.plot(titanic_fit, 
           yesno = 2, 
           fallen.leaves = TRUE, 
           faclen = 6, 
           digits = 4)
```


important variables:

- sex 
- pclass
- sib_sp

```{r}
rpart.rules(titanic_fit, cover = TRUE)
```

female in the upper or middle class has the highest chance of surviving

female in the lower class has the lowest chance of surviving


```{r}
library(modelr)

# add the predictions
titanic_test_pred <- titanic_test %>%
  add_predictions(titanic_fit, type = 'class')

titanic_test_pred <- titanic_test_pred %>% 
  mutate(survived = as_factor(survived))
```

```{r}
library(yardstick)

conf_mat <- titanic_test_pred %>%
              conf_mat(truth = survived, estimate = pred)

conf_mat

```

```{r}
accuracy <- titanic_test_pred %>%
 accuracy(truth = survived, estimate = pred)

accuracy 
```


```{r}
titanic_test_pred %>%
  sensitivity(truth = survived, estimate = pred)
```


```{r}
titanic_test_pred %>%
  specificity(truth = survived, estimate = pred)
```

```{r}
library(caret)

confusionMatrix(titanic_test_pred$pred, titanic_test_pred$survived)
```

