---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(fastDummies)
library(GGally)
library(ggfortify)
library(mosaic)
library(mosaicData)
library(corrplot)
```



#########
read in data
#########

```{r}
housing_prices <- read_csv("data/housing_prices.csv")
housing_prices
```


Notes: 

what does one row represent? An aggregate of a district in California

some variables are row sums, some are "stats", like averages 
--> do some feature engineering / variable transformation to get more "stats"
that are meaningful to me about these houses

Lets do some feature engineering
- the data set we start with is the "raw material"
- We can use those to make more meaning, aid interpretation


```{r}
house <- housing_prices %>% 
  mutate(bedrooms_per_house = total_bedrooms / households, 
         rooms_per_house = total_rooms / households,
         people_per_house = population / households,
         bedrooms_per_person = total_bedrooms / population, 
         rooms_per_person = total_rooms / population,
         bedrooms_per_room = total_bedrooms / total_rooms,
         non_bedrooms_per_house = rooms_per_house - bedrooms_per_house)
```

```{r}
skimr::skim(house)

glimpse(house)
```


extra idea: start using long & lats to make more meaning 
--> joining to external city coordinate data, creating labels, flags, or 
things 

```{r message=FALSE}

ggpairs1 <- house %>% 
  select(housing_median_age,median_income,median_house_value,ocean_proximity)
  
  
ggpairs(ggpairs1)


ggpairs2 <- house %>% 
  select(median_house_value, total_rooms, rooms_per_house, total_bedrooms, bedrooms_per_house) 


ggpairs(ggpairs2)


ggpairs3 <- house %>% 
  select(median_house_value,
         households,
         population,
         people_per_house,
         total_rooms,
         rooms_per_house)

ggpairs(ggpairs3)
```


household assumption - "Proxy" for being in an urban/city area

```{r}
house %>% 
  select_if(is.numeric) %>% 
  skimr::skim()

  
```

```{r}
library(raster)
library(leaflet)

raster <- rasterFromXYZ(housing_prices %>% 
  dplyr::select(longitude, latitude, median_house_value), crs = "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

pal <- colorNumeric(c("blue", "red", "yellow"), values(raster),
  na.color = "transparent")

leaflet() %>% 
  addTiles() %>% 
  addRasterImage(raster, colors = pal, opacity = 0.7) %>% 
  addLegend(pal = pal, values = values(raster),
    title = "Median House Value")
```


Log Transformations - truncates data - helps with skewed data

```{r}
ggplot(house, aes(log(median_income)))+ 
  geom_histogram() +
  theme_classic()
```


#########
task 1
#########

```{r}
ggpairs(housing_prices, columns = c("total_rooms", "total_bedrooms"))
```

they are strongly correlated with a correlation coefficient of 0.934

linear distribution 

very skewed to the right 

########
task 2
########

```{r}
housing_prices <- housing_prices %>% 
  select(-c(total_bedrooms))

housing_prices <- housing_prices %>% 
  select(-c(longitude, latitude))
```


#########
task 3
#########

```{r message=FALSE}
ggpairs(housing_prices)

# correlation matrix doesnt work with boolean variable
corrplot()

```

```{r}

# plot housebolds ~ total rooms

housing_prices %>% 
  ggplot(aes(total_rooms, households)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

# households ~ population

housing_prices %>% 
  ggplot(aes(population, households)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

# population ~ total_rooms 

housing_prices %>% 
  ggplot(aes(total_rooms, population)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

# median_house_value ~ median_income

housing_prices %>% 
  ggplot(aes(median_income, median_house_value)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

```

########
task 4
########

```{r}
housing_prices %>% 
  distinct(ocean_proximity)

housing_prices %>% 
  fastDummies::dummy_cols(select_columns = "ocean_proximity",
                          # avoid dummy variable trap
                          remove_first_dummy = TRUE, 
                          # remove original col
                          remove_selected_columns = TRUE)
  

# 5 dummy variables expected, but will have to drop one to avoid multicollinearity
```

##########
task 5
##########

```{r}
# regress median_house_value ~ median_income

lm1 <- lm(median_house_value ~ median_income, data = housing_prices)

summary(lm1)

par(mfrow = c(2,2))
plot(lm1)
```

- residuals vs fitted - flat line indicates that there is a good random scattering
therefore residuals are independent
- normal q-q - line shows a fairly straight line indicating a normal distribution
- scale-location - residuals appear fairly randomly spread which satisfies the 
assumption of homoskedasticity
- residuals vs leverage - cant see any cook's distance lines therefore the outlier
cases are not influential 


########
task 6 
########

```{r}
lm2 <- lm(median_house_value ~ median_income + housing_median_age, data = housing_prices)

summary(lm2)

par(mfrow = c(2,2))
plot(lm2)
```

diagnostics fairly similar to before, better fit for assumption of homoskedasticity 

```{r}
lm2
```

results suggest a 1 unit increase in median_income is associated with a 42420
increase in median_house_value, holding all other factors constant.  

a 1 unit increase in housing_median_age is associated with a 1568 increase in 
median_house_age, holding all other factors constant. 


##########
Extension
##########

##########
task 1
##########



```{r}
lm3 <- lm(median_house_value ~ log(median_income) + housing_median_age + 
            population + log(median_income):housing_median_age, data = housing_prices)

autoplot(lm3)

lm3
```


I would say the predicator is justified given that it would be expected that
given a person's age, they are more likely to have a higher income -- having a 
greater impact on the median housing price. 

should probably change median_house_value to natural logarithm to counter a 
non-linear distribution for a more accurate model. 


#########
task 2 
#########

```{r}
coplot(median_house_value ~ log(median_income) | housing_median_age,
       rows = 1,
       panel = function(x, y, ...) {
         points(x, y)
         abline(lm(y ~ x), col = 4)
       },
       housing_prices)
```

As age increases we see a greater correlation between median_house_value ~ log(median_income)
gradient change is not that noticable




# log - log transformation model 

```{r}
lm4 <- lm(log(median_house_value) ~ log(median_income) + log(housing_median_age) 
          + ocean_proximity, data = housing_prices)

autoplot(lm4)

summary(lm4)
```


visualise skew: 

```{r}
housing_prices %>% 
  ggplot(aes(log(median_house_value))) +
  geom_histogram()
```


```{r}
library(leaflet)
```

```{r}
housing_prices %>% 
  leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(lng = ~longitude, lat = ~latitude,
                  clusterOptions = markerClusterOptions(maxClusterRadius = 50))
```

