---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(fastDummies)
library(GGally)
library(ggfortify)
library(mosaic)
library(mosaicData)
library(corrplot)
```


#########
read in data
#########

```{r}
housing_prices <- read_csv("data/housing_prices.csv")
housing_prices
```

#########
task 1
#########

```{r}
ggpairs(housing_prices, columns = c("total_rooms", "total_bedrooms"))
```

they are strongly correlated with a correlation coefficient of 0.934

########
task 2
########

```{r}
housing_prices <- housing_prices %>% 
  select(-c(total_bedrooms))

housing_prices <- housing_prices %>% 
  select(-c(longitude, latitude))
```


#########
task 3
#########

```{r message=FALSE}
ggpairs(housing_prices)

# correlation matrix doesnt work with boolean variable
corrplot()

```

```{r}

# plot housebolds ~ total rooms

housing_prices %>% 
  ggplot(aes(total_rooms, households)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

# households ~ population

housing_prices %>% 
  ggplot(aes(population, households)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

# population ~ total_rooms 

housing_prices %>% 
  ggplot(aes(total_rooms, population)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

# median_house_value ~ median_income

housing_prices %>% 
  ggplot(aes(median_income, median_house_value)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

```

########
task 4
########

```{r}
housing_prices %>% 
  distinct(ocean_proximity)

housing_prices %>% 
  fastDummies::dummy_cols(select_columns = "ocean_proximity",
                          # avoid dummy variable trap
                          remove_first_dummy = TRUE, 
                          # remove original col
                          remove_selected_columns = TRUE)
  

# 5 dummy variables expected, but will have to drop one to avoid multicollinearity
```

##########
task 5
##########

```{r}
# regress median_house_value ~ median_income

lm1 <- lm(median_house_value ~ median_income, data = housing_prices)

summary(lm1)

par(mfrow = c(2,2))
plot(lm1)
```

- residuals vs fitted - flat line indicates that there is a good random scattering
therefore residuals are independent
- normal q-q - line shows a fairly straight line indicating a normal distribution
- scale-location - residuals appear fairly randomly spread which satisfies the 
assumption of homoskedasticity
- residuals vs leverage - cant see any cook's distance lines therefore the outlier
cases are not influential 


########
task 6 
########

```{r}
lm2 <- lm(median_house_value ~ median_income + housing_median_age, data = housing_prices)

summary(lm2)

par(mfrow = c(2,2))
plot(lm2)
```

diagnostics fairly similar to before, better fit for assumption of homoskedasticity 

```{r}
lm2
```

results suggest a 1 unit increase in median_income is associated with a 42420
increase in median_house_value on average 

a 1 unit increase in housing_median_age is associated with a 1568 increase in 
median_house_age on average


##########
Extension
##########

##########
task 1
##########



```{r}
lm3 <- lm(median_house_value ~ log(median_income) + housing_median_age + population + log(median_income):housing_median_age, data = housing_prices)

autoplot(lm3)

lm3
```


I would say the predicator is justified given that it would be expected that
given a person's age, they are more likely to have a higher income -- having a 
greater impact on the median housing price. 

should probably change median_house_value to natural logarithm to counter a 
non-linear distribution for a more accurate model. 


#########
task 2 
#########

```{r}
coplot(median_house_value ~ log(median_income) | housing_median_age,
       rows = 1,
       panel = function(x, y, ...) {
         points(x, y)
         abline(lm(y ~ x), col = 4)
       },
       housing_prices)
```

As age increases we see a greater correlation between median_housing_value ~ log(median_income)